`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-16 inst/manuscript/manuscript.rmd
Remove xlim (and all references to it, as the new dataset does NOT contain an outlier requiring it;

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 2A)
scramblase_assay_plot(
  "inputTable.txt") +
xlim(0, 3)
```

```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(x) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
figure2
```

```{r calculate_pprs, echo = FALSE}
max_PPR <- utils::read.delim(
    file.path(tmpDir,"inputTable.txt"),
    check.names = FALSE) %>%
  flippant:::calculate_ppr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```

The call results in the protein to phospholipid ratio (PPR) plot shown in
Figure 2A. Using the customization facilities provided by `ggplot2` 
[@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
avoid visual compression of all data by a single data point from the wild type 
rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$.

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 2B)
scramblase_assay_plot(
  "inputTable.txt",
  split_by_experiment = FALSE) + 
xlim(0, 3)
```

>>>>

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 2A)
scramblase_assay_plot("inputTable.txt")
```

```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(x) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
figure2
```

The call results in the protein to phospholipid ratio (PPR) plot shown in
Figure 2A.

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 2B)
scramblase_assay_plot(
  "inputTable.txt",
  split_by_experiment = FALSE)
```
